Impact of cosmic variance on the galaxy-halo connection for Lyman-$\alpha$ emitters

### 2016-06-14 paper/ms.tex
typos

\begin{document}
%=========================================================================
%		FRONT MATTER
%=========================================================================
\title{Uncertainty on the galaxy-halo connection for Lyman-$\alpha$ emitters at $z=3.1$}
\author{
  Juli\'an E. Mej\'ia-Restrepo \thanks{jemejia@das.uchile.cl}$^{1,3}$,
  Jaime E. Forero-Romero \thanks{je.forero@uniandes.edu.co}$^{2}$ 
}

@@

We chose this simulation based on three requirements. 
First, the simulation has cosmological parameters consistent
with the most recent constraints from Cosmic Microwave Background
experiments and provide public acces to the data.
Second, the halo mass function from the simulation is robust
down to  $10^{10}$\hMsun, which is the lower halo mass bound suggested
by previous observational 
studies \citep{Hayashino2004,Gawiser2007,Ouchi2010,Bielby16}. 
Third, the total volume of the simulation is at least 10 times
larger than the equivalent volume of a single LAE observational field.
These conditions are met as we describe below.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.85\textwidth]{fig3.pdf}
\end{center}
\caption{One and two dimensional projections of the posterior
  probability distributions of \mmin, \mmax\ and \focc. 
  Vertical lines in the one dimensional proyections correspond to the
  14-50,84 percentiles of the distribtions.
  Thick lines in the two dimensional planes mark the 1-2-3 $\sigma$
  contours of the corresponding joint distributions.
  The models with $\log \focc>0.00$ ($\focc>1$) correspond  to models
  where the number density  of halos is smaller than the number of
  observed LAEs but we consider them as consistent because of the uncertainty
  in the median number density due to cosmic variance. See 
Fig. \ref{fig:cosmicv0} and \S\ref{subsec:explore} for details.} 
\label{fig:like}
\end{figure*}

@@

The authors acknowldge the referee, Nelson Padilla, for useful
remarks and questions that helped us to improve the quality and
clarity of our paper.

>>>>

\begin{document}
%=========================================================================
%		FRONT MATTER
%=========================================================================
\title{Impact of cosmic variance on the galaxy-halo connection for Lyman-$\alpha$ emitters}
\author{
  Juli\'an E. Mej\'ia-Restrepo \thanks{jemejia@das.uchile.cl}$^{1,3}$,
  Jaime E. Forero-Romero \thanks{je.forero@uniandes.edu.co}$^{2}$ 
}

@@

We chose this simulation based on three requirements. 
First, the simulation has cosmological parameters consistent
with the most recent constraints from Cosmic Microwave Background
experiments and provide public access to the data.
Second, the halo mass function from the simulation is robust
down to  $10^{10}$\hMsun, which is the lower halo mass bound suggested
by previous observational 
studies \citep{Hayashino2004,Gawiser2007,Ouchi2010,Bielby16}. 
Third, the total volume of the simulation is at least 10 times
larger than the equivalent volume of a single LAE observational field.
These conditions are met as we describe below.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.85\textwidth]{fig3.pdf}
\end{center}
\caption{One and two dimensional projections of the posterior
  probability distributions of \mmin, \mmax\ and \focc. 
  Vertical lines in the one dimensional projections correspond to the
  14-50,84 percentiles of the distributions.
  Thick lines in the two dimensional planes mark the 1-2-3 $\sigma$
  contours of the corresponding joint distributions.
  The models with $\log \focc>0.00$ ($\focc>1$) correspond  to models
  where the number density  of halos is smaller than the number of
  observed LAEs but we consider them as consistent because of the uncertainty
  in the median number density due to cosmic variance. See 
Fig. \ref{fig:cosmicv0} and \S\ref{subsec:explore} for details.} 
\label{fig:like}
\end{figure*}

@@

The authors acknowledge the referee, Nelson Padilla, for useful
remarks and questions that helped us to improve the quality and
clarity of our paper. The authors also acknowledge Valentino Gonzalez,
Eric Gawiser and Mark Dijkstra for the fruitful discussion and
suggestions that also contributed to improve the quality of this work.
